---
title: Title of Presentation
author: Alice Jones
institute: Center for Statistics, Agency A
date: now
thanks: |
  Joint work with **Bob Smith** (University of A) and
  **Curtis Johnson** (University of B).
format:
  beamer:
    mathspec: true
    colorlinks: true
    link-citations: true
    section-titles: false
    linkcolor: blue
    include-in-header:
      text: |
        \usepackage{slides}
pdf-engine: pdflatex
code-block-border-left: "#008CFF"
bibliography: ../bib/references.bib
echo: true
---

```{r}
#| echo: false
source("setup.R")
```

## TBD

- See if we can remove footnote marker from `thanks`.

- For the bibliography
	+ Make the text black. The code I had had for the previous template does not work here ...
	+ Make the text smaller. I have a workaround for now

- Make the footer information into nonlinks that render in black.

# Intro

## Introduction

- This is example of slides.
- Here is a citation to R [@Rcore] and Latex [@Lamport1986]. 

## Some Customizations

1. Add a bibliography.
1. Set the title/header font to serif to match the content.
1. Set the dimensions.
1. Add a footnote with the compile time, package version, and contact information.
1. Set the style of code displays.
1. Redefine Latex `\vec{...}` to make symbols bold.

# Code

## A Code Display

Here is a code chunk.

```{r}
x = rnorm(100)
head(x, 50)
```

Now $\vec{x} = (x_1, \ldots, x_n)$ is a vector.

## A Plot

```{r}
hist(x)
```

## Another Slide with Bullets

- First point.
- Second point.
- Third point.


# Conclusions

## References {-}
\footnotesize
