---
title: The 'base' Package
author: Alice Jones, Bob Smith, & Curtis Johnson
date: now
thanks: >
  Document was compiled `{r} format(Sys.time(), "%Y-%m-%d %H:%M:%S %Z")` and
  corresponds to `base` version `{r} packageVersion("base")`.
  Alice Jones (<alice.jones@mail1.org>), Mailing Address 1.
  Bob Smith (<bob.smith@mail2.org>), Mailing Address 2.
  Curtis Johnson (<curtis.johnson@mail3.org>), Mailing Address 3.
format:
  pdf:
    mathspec: true
    fontsize: 10pt
    number-sections: true
    colorlinks: true
    link-citations: true
    # toc: true
    # toccolor: blue
    include-in-header:
      text: |
        \usepackage{common}
pdf-engine: pdflatex
geometry:
  - left=0.75in
  - right=0.75in
  - top=0.75in
  - bottom=1.00in
vignette: >
  %\VignetteIndexEntry{The 'base' Package}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{quarto::pdf}
code-block-border-left: "#008CFF"
bibliography: references.bib
---

```{r}
#| echo: false
# This prints the name of a function with its arguments
print_function = function(x) {
	desc = capture.output( str(x, give.attr = F) )
	out = sub(pattern = "function ", replacement = substitute(x), x = desc,
		fixed = TRUE)
	cat(paste(out, collapse = "\n"))
}
```

# Introduction

This is example of a package vignette for the `base` package in R [@Rcore].

```{r}
x = rnorm(100)
hist(x)
head(x, 20)
```

Now $\vec{x} = (x_1, \ldots, x_n)$ is a vector.

Here's a citation to Latex [@Lamport1986].

Some customizations are:

1. Add a bibliography.
1. Set the title/header font to serif to match the content.
1. Set the dimensions.
1. Add a footnote with the compile time, package version, and contact information.
1. Set the style of code displays.
1. Redefine Latex `\vec{...}` to make symbols bold.

# References {-}

